Addition and removal energies of circular quantum dots

### 2017-08-26 Manuscript/paper.tex
Add table for comparing against FCI

The energy of each single-particle state $|n m_\ell m_{\mathrm{s}}\rangle$ is given by
\begin{align} \label{eq:energysingleparticlestate}
  \varepsilon_{n m_\ell m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega.
\end{align}
They are degenerate with respect to both spin projection $m_{\mathrm{s}}$ and \textit{shell index} $k$,
\begin{align} \label{eq:shell_index}
  k \equiv 2 n + |m_\ell|,
\end{align}
which labels each shell from zero.  The shell structure is illustrated in Figure \ref{fig:shell-structure}.

@@

The equations can be derived directly from the anticommutation relations of the creation and annihilation operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.  In particular, Figure \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}.

@@

In practice, the cluster operator $\hat{T}$ must be truncated for calculations to be computationally feasible.  In this work, we use only single and double excitations,
\begin{align*}
  \hat{T} = \hat{T}_1 + \hat{T}_2.
\end{align*}
This is known as coupled cluster with singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).  This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{2014RPPh...77i6302H}.  In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.  Figure \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.\ \eqref{eq:cc_heff1} in CCSD.

@@

We can then express the perturbation expansion in terms of summations over matrix elements as we did for the IM-SRG flow equation, again with the aid of Wick's theorem or diagrammatic techniques.  This leads to the following expression for the second-order correction:
\begin{align*}
  \varepsilon_p^{(2)}
  &=
    \sum_{i a b} \frac{|H_{p i a b}|^2}{2 \Delta_{p i a b}}
    - \sum_{i j a} \frac{|H_{i j p a}|^2}{2 \Delta_{i j p a}},
\end{align*}
where the M\o ller--Plesset denominators $\Delta$ are defined in Eq.\ \eqref{eq:moellerplessetdenominator}.  The above expression is depicted in Figure \ref{fig:diagrams-sfe}.  Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Figure \ref{fig:diagrams-sfe}.  We will refer to QDPT to third order as ``QDPT3''.

@@

Afterward, there are several paths through which one can traverse Figure \ref{fig:methods} to obtain output observables.  We shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.

@@

All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Figure \ref{fig:shell-structure} for an illustration of the shell structure).  This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).  Addition/removal energies $\varepsilon^{(\pm)}$ are similarly restricted in that we only calculate the energy difference between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same system but with one particle added/removed:
\begin{align*}
  \varepsilon^{(+)} &\equiv E_{(N + 1)} - E_N, \\
  \varepsilon^{(-)} &\equiv E_N - E_{(N - 1)}.
\end{align*}

@@

In Fig.\ \ref{fig:gs} we display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.  We also include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} for comparison where available.

>>>>

The energy of each single-particle state $|n m_\ell m_{\mathrm{s}}\rangle$ is given by
\begin{align} \label{eq:energysingleparticlestate}
  \varepsilon_{n m_\ell m_{\mathrm{s}}} \equiv (2 n + |m_\ell| + 1) \omega.
\end{align}
They are degenerate with respect to both spin projection $m_{\mathrm{s}}$ and \textit{shell index} $k$,
\begin{align} \label{eq:shell_index}
  k \equiv 2 n + |m_\ell|,
\end{align}
which labels each shell from zero.  The shell structure is illustrated in Fig.\ \ref{fig:shell-structure}.

@@

The equations can be derived directly from the anticommutation relations of the creation and annihilation operators, but it is more convenient to use Wick's theorem \cite{PhysRev.80.268} or, even more efficiently, diagrammatic techniques \cite{shavitt2009many} to arrive at the results.  In particular, Fig.\ \ref{fig:diagrams-imsrg} shows the diagrammatic form of Eq.\ \eqref{eq:flow0}, Eq.\ \eqref{eq:flow1}, and Eq.\ \eqref{eq:flow2}.

@@

In practice, the cluster operator $\hat{T}$ must be truncated for calculations to be computationally feasible.  In this work, we use only single and double excitations,
\begin{align*}
  \hat{T} = \hat{T}_1 + \hat{T}_2.
\end{align*}
This is known as coupled cluster with singles and doubles (CCSD), with an asymptotic computational cost that scales like IM-SRG(2).  This truncation has been successfully applied to many problems in quantum chemistry \cite{RevModPhys.79.291} and nuclear physics \cite{2014RPPh...77i6302H}.  In addition, we also truncate the three-body effective Hamiltonian terms that are induced by the similarity transformation.  Fig.\ \ref{fig:diagrams-ccsd} shows the diagrammatic representation of Eq.\ \eqref{eq:cc_heff1} in CCSD.

@@

We can then express the perturbation expansion in terms of summations over matrix elements as we did for the IM-SRG flow equation, again with the aid of Wick's theorem or diagrammatic techniques.  This leads to the following expression for the second-order correction:
\begin{align*}
  \varepsilon_p^{(2)}
  &=
    \sum_{i a b} \frac{|H_{p i a b}|^2}{2 \Delta_{p i a b}}
    - \sum_{i j a} \frac{|H_{i j p a}|^2}{2 \Delta_{i j p a}},
\end{align*}
where the M\o ller--Plesset denominators $\Delta$ are defined in Eq.\ \eqref{eq:moellerplessetdenominator}.  The above expression is depicted in Fig.\ \ref{fig:diagrams-sfe}.  Since there are numerous terms in the third-order correction $\varepsilon_p^{(3)}$, they are listed in diagrammatic form in Fig.\ \ref{fig:diagrams-sfe}.  We will refer to QDPT to third order as ``QDPT3''.

@@

Afterward, there are several paths through which one can traverse Fig.\ \ref{fig:methods} to obtain output observables.  We shall primarily focus on the three combinations: (a) HF + IM-SRG(2) + QDPT3, (b) HF + IM-SRG(2) + EOM2, and (c) HF + CCSD + EOM2.

@@

All calculations of ground state energy $E_N$ in this paper are restricted to cases where the number of particles $N$ is a magic number, i.e.\ a \textit{closed shell} system (see Fig.\ \ref{fig:shell-structure} for an illustration of the shell structure).  This is a limitation of the many-body methods used in this paper and while there are ways to overcome this limit they are beyond the scope of this paper (see Section \ref{sec:conclusions} for some ideas).  Addition/removal energies $\varepsilon^{(\pm)}$ are similarly restricted in that we only calculate the energy difference between $E_N$ of a closed shell system and $E_{N \pm 1}$ of the same system but with one particle added/removed:
\begin{align*}
  \varepsilon^{(+)} &\equiv E_{(N + 1)} - E_N, \\
  \varepsilon^{(-)} &\equiv E_N - E_{(N - 1)}.
\end{align*}

@@

\begin{table}
  \centering
  \caption{Similar to Table \ref{tab:ground}, this table compares the ground state energies of quantum dots calculated using IM-SRG(2), CCSD, and FCI \cite{olsen2013thesis}.}
  \label{tab:ground-fci}
  \input{tab-ground-fci}\unskip
\end{table}

Fig.\ \ref{fig:gs} and Table \ref{tab:ground} display a selection of ground state energies calculated using HF + IM-SRG(2) and HF + CCSD as described in Section \ref{subsec:methodology}.  We include results from M\o ller--Plesset perturbation theory to second order (MP2), DMC \cite{hoegberget2013thesis}, and FCI \cite{olsen2013thesis} (see Table \ref{tab:ground-fci}) for comparison where available.
